Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution

### 2018-05-10 manuscript.tex
Add files via upload

Fig.~\ref{fig:faculae} shows the results obtained when a faculae is present on the photosphere of the star. It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RVs for all the proposed indicators. SN mean RV seems to have the smallest spurious variations caused by the faculae. Anyway, the evaluation of the standard errors retrieved by using a bootstrap analysis that will be detailed discussed in Section \ref{sec:5}, shows that RV mean SN has the largest related uncertainties. The standard errors associates with RV median SN and RV are comparable, although the standard errors retrieved when the RV is defined as the median of the SN are $10 \%$ smaller than the standard errors derived for RV.

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_FACULAE.pdf} 
\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
   \caption{(left) RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV. RV mean SN has the largest related uncertainties.}
    \label{fig:faculae}
\end{figure*}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a faculae is present on the photosphere of the star. In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlation between the RVs and respectively the asymmetry parameter and the width parameter.}
    \label{fig:faculae.corr}
\end{figure*}

@@

Fig.~\ref{fig:spot} shows the results obtained when a spot is present on the photosphere of the star. Similarly to the previous case, the presence of the spot leads to spurious variations in RVs for all the proposed indicators, but N mean RV seems to have the smallest ones. The evaluation of the standard errors, as before, shows that RV mean SN has the largest variability, while the standard errors associated with RV median SN are $10 \%$ smaller than the standard errors associated with RV.

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_SPOT.pdf} 
\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
   \caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV. RV mean SN has the largest related uncertainties.}
    \label{fig:spot}
\end{figure*}

@@

Fig.~\ref{fig:spot.plus.planet} shows the results obtained when a spot is present on the photosphere of the star and a planet is injected. The planet, having an amplitude of 10 \ms, produces a pure doppler shift on the CCF, without further changing its shape.  In this case N mean RV seems to have the largest variations caused by the combined action of spot and planet. The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: RV mean SN has the largest related uncertainties and the standard errors associates with RV median SN are $10 \%$ smaller than the standard errors derived for RV.

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_PLANET_SPOT.pdf} 
\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
   \caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected. N mean RV seems to have the largest variations caused by the combined action of spot and planet. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV. RV mean SN has the largest related uncertainties}
    \label{fig:spot.plus.planet}
\end{figure*}

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 3in]{RV_comparison_PLANET.pdf} 
%\includegraphics[height = 2.5in]{SOAP_PLANET_Comparison_para_SN.pdf} 
   \caption{RVs changes as function of the orbital phase after removed the spurious effect of the spot. In green the real signal of the planet is displayed.}
    \label{fig:planet-spot}
\end{figure*}

In this Section we presented a first implementation of the SN fit to CCF, using the simulation environment SOAP. Before moving to the next Section, where the analyses on five real stars are presented, we need to provide further considerations. First of all, looking ad the analyses conducted with SOAP, it seems that the largest correlation between an asymmetry parameter and a set of RVs happens to be when respectively $\gamma$ and RV median SN are used. This is a bit surprising, since as the shape of the CCF changes, we expect RV median SN to be more robust than RV mean SN. \umberto{A possible justification of this ...}. As second, the standard errors that have been retrieved suggest that using RV median SN can minimize the uncertainties respect using both RV mean SN and RV. We will present details of this in Section \ref{sec:5}. As third, when searching for stellar activity by deriving the correlation between the set of RVs and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot. When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star. Finally, the correlations involving the common indicators (i.e. RV, FWHM and BIS SPAN) are systematically weaker than the correlations obtained by fitting the SN to the CCF, suggesting that this distribution could be helpful when searching for active regions. We recall moreover that all the quantities needed for conducting the analyses of the CCF are directly available by just fitting the SN.

@@

%%%%%% April 13th, 2018
%%% in the new Analyses we do not use the noise parameter
%%%%%%
\iffalse
The HARPS reduction pipeline gives the pure photon-noise error estimate on the RVs. This error, called \emph{noise}, is not derived from the Normal fit to the CCF but from the method described in \citet{Bouchy-2001b} using the CCF derivative. Then \emph{noise} is associated to the RV error, $2\times$\emph{noise} to the BIS SPAN error and $2.35\times$\emph{noise} to the FWHM error.
\fi
%%%%%%
%%%
%%%%%% April 13th, 2018

In this section, we perform a bootstrap analysis to measure the standard errors associated to RV mean SN, RV median SN, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point. To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF. We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV mean SN, RV median SN, RV), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry ($\gamma$ or BIS SPAN).
\comment{It is not clear what you are doing here. I can understand bootstrapping a time series: you shuffle all the values keeping the time stamps fixed. How do you bootstrap a stellar spectrum? Do you shuffle the intensity values keeping the wavelengths fixed? That would produce a mess. Do you just add different levels of random noise? But the spectra already have noise in them, they are real observations. You need to state more clearly here what you did.}

In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), RV mean SN (black circles) or RV median SN (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels. The parameter SN50 corresponds to the SNR in order 50, which defines a wavelength of 550\,nm. In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal distribution. We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type. This is true if the spectral type are not too different though, like here where we show the results for G and K dwarfs.

@@

\umberto{add discussions on SOAP example}

We compared for five stars the difference between the RVs (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case). The $\gamma$ parameter is linearly dependant on the BIS SPAN, with always a strong correlation coefficient. 
%To compare $\gamma$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma$ by the slope of the linear dependence between $\gamma$ and BIS SPAN. 
The slope of this linear correlation changes depending on the studied star. This is probably because the spectral type is different, therefore the effects from stellar activity are different.

When using as parameter for the RV the mean of the SN, the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal. However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN. Therefore, the SN parameters are more sensitive to activity. In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.436$ between $\gamma$ and RV mean SN, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.

@@

\umberto{add conclusions on SOAP example}

Using the SN to fit CCFs brings a significant improvement in probing stellar activity. While for the Normal distribution mean and median are equivalent, using the SN fit different location parameters can be tested. While the median of the SN is more robust respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF. We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter are $10\%$ smaller than the standard errors retrieved using the Normal distribution. For evaluating changes in the asymmetry of the CCF, we suggest to use the mean of the SN. The correlations between RV mean SN and SN FWHM, and RV mean SN and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}). The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%. Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.

>>>>

Fig.~\ref{fig:faculae} shows the results obtained when a faculae is present on the photosphere of the star. It is possible to note that, although there is not a planet, the presence of the faculae leads to spurious variations in RVs for all the proposed indicators. SN mean RV seems to have the smallest spurious variations caused by the faculae. %Anyway, the evaluation of the standard errors retrieved by using a bootstrap analysis that will be detailed discussed in Section \ref{sec:5}, shows that RV mean SN has the largest related uncertainties. The standard errors associates with RV median SN and RV are comparable, although the standard errors retrieved when the RV is defined as the median of the SN are $10 \%$ smaller than the standard errors derived for RV.

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{RV_comparison_FACULAE.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
\caption{(RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae.}
   %\caption{(left) RVs changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV. RV mean SN has the largest related uncertainties.}
    \label{fig:faculae}
\end{figure*}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{SOAP_FACULAE_Comparison_para_SN.pdf} 
   \caption{Evaluation of the correlation between the RVs and the asymmetry parameters when a faculae is present on the photosphere of the star. In this case both the shape and the width of the CCF changes as the faculae moves, producing statistically significative correlations between the RVs and respectively the asymmetry parameter and the width parameter.}
    \label{fig:faculae.corr}
\end{figure*}

@@

Fig.~\ref{fig:spot} shows the results obtained when a spot is present on the photosphere of the star. Similarly to the previous case, the presence of the spot leads to spurious variations in RVs for all the proposed indicators, but N mean RV seems to have the smallest ones. We note however that in this case all the three indicators are similarly effected by the spurious changes in RVs caused by the spot. %The evaluation of the standard errors, as before, shows that RV mean SN has the largest variability, while the standard errors associated with RV median SN are $10 \%$ smaller than the standard errors associated with RV.

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{RV_comparison_SPOT.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
\caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae.}
   %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV. RV mean SN has the largest related uncertainties.}
    \label{fig:spot}
\end{figure*}

@@

Fig.~\ref{fig:spot.plus.planet} shows the results obtained when a spot is present on the photosphere of the star and a planet is injected. The planet, having an amplitude of 10 \ms, produces a pure doppler shift on the CCF, without further changing its shape.  In this case N mean RV seems to have the largest variations caused by the combined action of spot and planet. %The evaluation of the standard errors leads to the same conclusions reported for the two previous cases: RV mean SN has the largest related uncertainties and the standard errors associates with RV median SN are $10 \%$ smaller than the standard errors derived for RV.

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{RV_comparison_PLANET_SPOT.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
 \caption{RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected. N mean RV seems to have the largest variations caused by the combined action of spot and planet.}
   %\caption{(left) RVs changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected. N mean RV seems to have the largest variations caused by the combined action of spot and planet. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for RV median SN are $10 \%$ smaller than the standard errors derived for RV. RV mean SN has the largest related uncertainties.}
    \label{fig:spot.plus.planet}
\end{figure*}

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{RV_comparison_PLANET.pdf} 
%\includegraphics[height = 2.5in]{SOAP_PLANET_Comparison_para_SN.pdf} 
   \caption{RVs changes as function of the orbital phase after removed the spurious effect of the spot. In green the real signal of the planet is displayed.}
    \label{fig:planet-spot}
\end{figure*}

In this Section we presented a first implementation of the SN fit to CCF, using the simulation environment SOAP. Before moving to the next Section, where the analyses on five real stars are presented, we need to provide further considerations. First of all, looking ad the analyses conducted with SOAP, it seems that the largest correlation between an asymmetry parameter and a set of RVs happens to be when respectively $\gamma$ and RV median SN are used. This is a bit surprising, since as the shape of the CCF changes, we expect RV median SN to be more robust than RV mean SN. \umberto{A possible justification of this ...}. As second, when searching for stellar activity by deriving the correlation between the set of RVs and either an asymmetry parameter or the width of the CCF, the latter leads to weaker and hence less conclusive results if the active region is a spot. When stellar activity is dominated by faculae, both the shape and the width of the CCF changes as the faculae evolves on the photosphere of the star. Finally, the correlations involving the common indicators (i.e. RV, FWHM and BIS SPAN) are systematically weaker than the correlations obtained by fitting the SN to the CCF, suggesting that this distribution could be helpful when searching for active regions. We recall moreover that all the quantities needed for conducting the analyses of the CCF are directly available by just fitting the SN.

We remand the reader to Section \ref{sec:5} for the evaluation of the standard errors associated with the parameters estimated for all the three presented cases. This step will point out how RV median SN minimizes the uncertainties respect using both RV mean SN and RV, therefore suggesting its use in order to properly define the set of RVs of the star.

@@

In this section, we perform a bootstrap analysis to measure the standard errors associated to RV mean SN, RV median SN, RV, FWHM, SN FWHM, BIS SPAN and $\gamma$. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Gaussian distribution scaled to the error of each given point. To bypass this problem, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF. We then fit a Normal or a SN to each of these CCFs and then calculate the standard deviations of the distribution for the location parameters (RV, RV mean SN or RV median SN), the width parameters (FWHM or SN FWHM) and the parameters of asymmetry (BIS SPAN or $\gamma$).
\comment{It is not clear what you are doing here. I can understand bootstrapping a time series: you shuffle all the values keeping the time stamps fixed. How do you bootstrap a stellar spectrum? Do you shuffle the intensity values keeping the wavelengths fixed? That would produce a mess. Do you just add different levels of random noise? But the spectra already have noise in them, they are real observations. You need to state more clearly here what you did.}

\subsection{Estimation of standard errors for the CCF parameters for the simulation study} \label{sec:bootstrap_soap}

We start by calculating the standard errors of the parameters retrieved in Section \ref{sec:soap}, where with SOAP we produced CCFs contaminated by a faculae or a spot. In the third and final case we considered, beyond the spot, a planetary signal that produces pure doppler shifts i the CCFs.

Fig.~\ref{fig:se.soap.faculae} shows the results of the bootstrap analysis performed when a faculae is present on the photosphere of the star. The series of three plots in the top of Fig.~\ref{fig:se.soap.faculae} show the different errors for the RVs, defined as RV (red triangles), RV mean SN (black circles) or RV median SN (cyan crosses), the width and the asymmetry of the CCFs. In the three plots in the bottomof Fig.~\ref{fig:se.soap.faculae} we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal distribution. Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.5$ when using RV mean SN and $0.9$ when using RV median SN. By using RV median SN we get standard errors $10\%$ smaller than using the Normal fit and its corresponding mean. Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable. Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF. Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $20\%$ smaller. Therefore, the SN fit gives a better precision in CCF asymmetry than what can be reached using BIS SPAN.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{RV_comparison_FACULAE_standard_errors.pdf} 
   \caption{Faculae Case. Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter. When using RV mean SN (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles). However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN. \umberto{explain what happens for those CCF 15 to 19 where s.e. decrease.} Note that for the asymmetry, the error in BIS SPAN is in \kms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se.soap.faculae}
\end{figure*}

Fig.~\ref{fig:se.soap.spot} shows the results of the bootstrap analysis performed when a spot is present on the photosphere of the star. The series of plots follows the specifications outlined for the previous case. Concerning the standard errors related to the RVs, the ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using RV mean SN and $0.9$ when using RV median SN. Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal and the SN are comparable. Therefore, the precision in the width of the CCF is the comparable if we fit a Normal or a SN to the CCF. Finally, for the errors in evaluating the asymmetry of the CCF, we see that, when fitting the SN to the CCF, the asymmetry errors are $20\%$ smaller.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{RV_comparison_SPOT_standard_errors.pdf} 
   \caption{Spot case. Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter. When using RV mean SN (black circles), the standard errors are in average $40\%$ larger than the standard errors retrieved fitting a Normal (red triangles). However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \kms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se.soap.spot}
\end{figure*}

Fig.~\ref{fig:se.soap.spot.planet} shows the results of the bootstrap analysis performed when a spot is present on the photosphere of the star. The series of plots follows the specifications outlined for the previous two cases. The conclusions are comparable to the case in which only a spot is present on the photosphere of the star. The ratio between the RV error measured by the bootstrap using the SN and Normal fitting is $1.4$ when using RV mean SN and $0.9$ when using RV median SN. The errors in width of the CCF are comparable and the errors in evaluating the asymmetry of the CCF are $20\%$ smaller when using the asymmetry parameter $\gamma$ of the SN.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{RV_comparison_SPOT_PLANET_standard_errors.pdf} 
   \caption{Spot and Planet case. Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameter. When using RV mean SN (black circles), the standard errors are in average $50\%$ larger than the standard errors retrieved fitting a Normal (red triangles). However, if using RV median SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. To use as asymmetry parameter $\gamma$ of the SN leads to standard errors in average $20\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \kms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se.soap.spot.planet}
\end{figure*}

\subsection{Estimation of standard errors for the CCF parameters for real stars} \label{sec:bootstrap_real_star}
In the top plots of Fig.~\ref{fig:se} we show the different errors for the RVs, either defined as RV (red triangles), RV mean SN (black circles) or RV median SN (cyan crosses), the width and the asymmetry of the CCFs for three star, HD215152, HD192310 and Corot-7, that are all at different SNR levels. The parameter SN50 corresponds to the SNR in order 50, which defines a wavelength of 550\,nm. In the bottom plots, we show the ratio between the parameters derived from the bootstrap analysis fitting the SN and the parameters derived from the bootstrap analysis fitting the Normal distribution. We first see that the errors on the CCF parameters only depends on the SNR and do not depend on the spectral type. This is true if the spectral type are not too different though, like here where we show the results for G and K dwarfs.

@@

We tested at first our assumptions by using simulated CCFs retrieved using the software SOAP 2.0. We then compared for five real stars the difference between the RVs (defined as mean of a Normal, mean of the SN or median of the SN), FWHM and asymmetry (BIS SPAN in the Normal case and $\gamma$ in the SN case). The $\gamma$ parameter is linearly dependent on the BIS SPAN, with always a strong correlation coefficient. 
%To compare $\gamma$, that do not have any units, with BIS SPAN expressed in \kms, one has simply to multiply $\gamma$ by the slope of the linear dependence between $\gamma$ and BIS SPAN. 
The slope of this linear correlation changes depending on the studied star. This is probably because the spectral type is different, therefore the effects from stellar activity are different.

When using as parameter for the RV the mean of the SN, the standard errors are in average $60\%$ larger than the standard errors retrieved fitting a Normal. However, once the RV is defined as the median of the SN (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. When looking at the correlation between the asymmetry and width parameters of the CCF (FWHM and BIS SPAN or the alternative indicators in \citet{Figueira-2013} in the Normal case, and SN FWHM and $\gamma$ in the SN case) with respect to the RVs (RVs in the Normal case or SN RVs in the SN case), we observe that the correlations are always stronger for the parameters of the SN. Therefore, the SN parameters are more sensitive to activity. In the case of Tau Ceti, which is at very low activity level, we find a significant correlation of $0.322$ between $\gamma$ and RV mean SN, while for all the other asymmetric parameterization, BIS SPAN or the alternative indicators in \citet{Figueira-2013}, the correlations are weaker with a maximum of 0.$225$.

@@

Starting from the simulation environment SOAP and then moving to real stars, we showed that using the SN distribution to fit CCFs brings a significant improvement in probing stellar activity. While for the Normal distribution mean and median are equivalent, using the SN fit different location parameters can be tested. While the median of the SN is more robust respect variations in the shape of the CCF, the mean of the SN is more sensible to changes in the asymmetry of the CCF. We suggest to use as parameter that defines the RV of the star the median of the SN, since the standard errors related to this parameter are $10\%$ smaller than the standard errors retrieved using the Normal distribution. For evaluating changes in the asymmetry of the CCF, we suggest to use the mean of the SN. The correlations between RV mean SN and SN FWHM, and RV mean SN and $\gamma$ (the asymmetry parameter of the SN) are much stronger than the correlations between the equivalent parameters derived using a Normal fit (RV, FWHM and BIS SPAN or the asymmetric parameters described in \citet{Figueira-2013}). The precision on the asymmetry measured by $\gamma$ is greater than the one on BIS SPAN by $\sim$15\%. Therefore when searching for rotational periods in the data, or applying Gaussian Processes to account for stellar activity signals, the SN parameters should be used.
